Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-06 paper/intro.tex
"compared to" => "compared with"
Paper update

For analog circuits, the design parameters like widths and lengths of
transistors are manually calculated by designers with their experience and the
understanding of the design specifications. However, due to the progress of IC
manufacture technology forecasted by Moore's law, the circuit devices become
more and more complicated, and the parasitic effect of the circuit can no
longer be ignored; on the other hand, the demands for high-performance,
low-power analog circuits is increasing. It is getting much more difficult to
meet the performance and time-to-market requirement with manual designing.
Automated analog circuit design has thus attracted much research interests in
the past decade~\cite{rutenbar2007hierarchical}.

% TODO: Traditional methods using offline model and simulated based methods are
% not good
The analog circuit design automation problems can be formulated as optimization
problems, the aim is to find the optimal vector of design parameters that give
the best figure of merit (FOM). Prior works about analog circuit optimization
include offline model-based approaches
~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
simulation-based approaches. The offline model-based methods try to build
accurate global models and then optimize the cheap-to-evaluate models. The
model either comes from designers' manual derivation or regression models like
SVM and ANN. The problem of this approach is that the accurate models are
usually hard to get; for example, in~\cite{wang2014enabling}, 100,000 randomly
simulated points are used to train a sparse polynomial model for an amplifier
circuit with ten design parameters.

@@

The Bayesian optimization algorithm is a well-studied algorithm and has
demonstrated to be a promising algorithm for automated analog circuit design.
However, the standard Bayesian optimization algorithm is sequential; it chooses
the next evaluation point by optimizing the specified acquisition function,
which makes the parallelization of Bayesian optimization non-trivial. The
sequential property of BO limits its further application in multi-core computer
systems.

% TODO: Review current methods
% TODO: See how other papers review existing batch BO methods
Batch Bayesian optimization has been a hot topic in the BO literature.
Related works include the simulation matching (SM)
method~\cite{azimi2010batch}, the BUCB (BLCB for minimization)
method~\cite{desautels2014parallelizing}, the GP-UCB-PE
method~\cite{contal2013parallel}, the local penalization (LP)
method~\cite{gonzalez2016batch}, the parallel predictive entropy (PPES)
search~\cite{shah2015parallel} and the qKG method~\cite{wu2016parallel}.

\textcolor{red}{TODO}{Discuss more details about these algorithms}

% BUCB, UCB-PE: regret bound
% PPES: entropy search
% qKG, qEI: optimal decision if multiple points are selected
% LP: very good heuristic

@@

The MACE algorithm is tested using several analytical benchmark functions and
two real-world analog circuits, including an operational amplifier with ten
design parameters and a class-E power amplifier with twelve design parameters.
The BLCB method, local penalization method with expected improvement
acquisition function (EI-LP), qEI methods and qKG methods are compared with
MACE. The proposed MACE method achieved competitive performance when compared
to the listed state-of-the-art algorithms.

>>>>

For analog circuits, the design parameters like widths and lengths of
transistors are manually calculated by designers with their experience and the
understanding of the design specifications. However, due to the progress of IC
manufacture technology forecasted by Moore's law, the circuit devices become
more and more complicated, and the parasitic effect of the circuit can no
longer be ignored; on the other hand, the demands for high-performance,
low-power analog circuits is increasing. It is getting much more difficult to
meet the performance and time-to-market requirement with manual circuit analysis.
Automated analog circuit design has thus attracted much research interest in
the past decade~\cite{rutenbar2007hierarchical}.

% TODO: Traditional methods using offline model and simulated based methods are
% not good
The analog circuit design automation problems can be formulated as optimization
problems, the aim is to find the optimal vector of design parameters that gives
the best circuti performance, which is represented by a figure of merit (FOM)
function. Prior works about analog circuit optimization include offline
model-based approaches
~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
simulation-based approaches. The offline model-based methods try to build
accurate global models and then optimize the cheap-to-evaluate models. The
problem of this approach is that the accurate models are usually hard to get;
for example, in~\cite{wang2014enabling}, 100,000 randomly simulated points are
used to train a sparse polynomial model for an amplifier circuit with ten
design parameters.

@@

The Bayesian optimization algorithm is a well-studied algorithm and has
demonstrated to be promising for the automated design of analog circuits.
However, the standard Bayesian optimization algorithm is sequential, it chooses
only one point at each iteration by optimizing the acquisition function. It is
often desirable to select a batch of points at each iteration, the sequential
property of BO limits its further application in multi-core computer systems.

The Bayesian optimization algorithm has been extended to enable batch
selection. Some prior works, like the qEI\cite{qEI}, qKG\cite{wu2016parallel}
and parallel predictive entropy search (PPES)~\cite{shah2015parallel}
approaches, consider to search for the optimal batch selection for a given
acquisition function. These methods usually involve some approximations or
Monte-Carlo sampling, and thus scales poorly as the batch size increases. Other
works, including the simulation matching (SM)~\cite{azimi2010batch} method, the
batch-UCB(BUCB, BLCB for minimization
problems)~\cite{desautels2014parallelizing} method, the parallel UCB with pure
exploration (GP-UCB-PE)~\cite{contal2013parallel} method and the local
penalization~\cite{gonzalez2016batch} method, adopted the \emph{greedy}
strategies that select individual points until the batch is filled.

@@

The MACE algorithm is tested using several analytical benchmark functions and
two real-world analog circuits, including an operational amplifier with ten
design parameters and a class-E power amplifier with twelve design parameters.
The BLCB method, local penalization method with expected improvement
acquisition function (EI-LP), qEI methods and qKG methods are compared with
MACE. The proposed MACE method achieved competitive performance when compared
with the listed state-of-the-art algorithms.
